---
title: "Handling folders of base called sequence output"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Preamble

This `base called sequence` vignette introduces how the sequence data prepared
by MinKNOW or Dorado may be processed in a simplified manner.

## Getting started with the canned dataset

The `rtqc` package is distributed with some simplified data.

```{r load_rtqc}
library(rtqc)

dorado_fastq_path <- get_bundled_path("fastq_pass")
bf <- basecalled_folder$new(dorado_fastq_path)
print(bf)
```

All that the `basecalled_folder` class instantiation has performed is to 
identify and validate that there are indeed sequence data that may have been
prepared by an Oxford Nanopore Technologies basecalling software. One of the
more useful next steps would be to question what these files actually are?

The class `get_list()` function will report the sequence files observed and some
of their metadata.

```{r get_file_tibble}
bf$get_sequence_file_info()

# we can also get just the files with complete paths as a vector; lists are
# good for slicing ...
bf$list_files()
```


The objective here is not to just identify files; but to parse salient
information from them. The `basecalled_folder` class provides method to index
these sequence files.

```{r parse_fastq}
single_fastq <- bf$list_files()[1]
index_tuple <- rtqc::index_fastq(single_fastq, tempdir())
#indexing returns a pair vector of original file and parquet index
print(index_tuple[2])
```

There's not much point in the indexing of the file if we can't read the file
contents; the parquet files prepared can be simply opened with e.g.

```{r open_parquet}
sequencing_summary <- arrow::read_parquet(index_tuple[2])
print(sequencing_summary)
```

These metrics read from the `parquet` file summary are used by other methods
such as those presented through `sequence_set` R6 class. This vignette is
intended to describe just the basics of handling folders of sequence
information. 

What is salient to mention here is that processing sequence files one at the
time is a little silly; analyses should be performed in bulk and ideally as a
non-blocking background process. This should be achieved using the methods
provided - the `index` method provided will facilitate indexing of multiple
sequence files in a background process - the `status` and `is_new_sequence_data`
methods provide additional methods for checking whether the indexing is ongoing
and whether new sequence files have become available within the sequencing
folder (e.g. during live basecalling).

```{r bulk_process}
bf$index(threads=3)
bf$status(echo=TRUE)

bf$is_new_sequence_data()
```

The exploration of the sequence dataset can be achieved using the R6 class,
`sequence_set`. A helpful constructor is provided within our `basecalled_folder`

```{r create_sequence_set}
sequence_set <- bf$as_sequence_set()
print(sequence_set)
```

For further information please read the next vignette in this package's series.

