---
title: "The sequence_set_summary R6 class"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Preamble

The `sequence_set_summary` is an object that presents sequence characteristics
that have been aggregated in a `sequence_set`. This R6 class contains the
methods that extract value from the data.frames that are encapsulated within
the `sequence_set` but which cannot be processed or interrogated.

## Getting started with the canned dataset

The `rtqc` package is distributed with some simplified data. In the first 
vignettes from the series accompanying this package, we prepared a 
`sequence_set` from a `basecalled_folder`. Whilst we can sequentially prepare
such a `sequence_set_summary` - the class also provides a simplified 
fast-forward constructor to streamline this process.

```{r load_rtqc}
library(rtqc)

dorado_fastq_path <- get_bundled_path("fastq_pass")
seq_summary <- sequence_set_summary$new(dorado_fastq_path, threads=2)
print(seq_summary)

print(seq_summary$get_sequence_set()$data)
```

